Kindly Bent to Free Us

### 2020-02-28 kindly/extensions.tex
Fix some bits about non-lexical regions.

\subsection{Algebraic Data Types}

Algebraic data types are a staple of functional programming and fit nicely
in our paradigm. Indeed, it is sufficient to check that the kinds of constructors
are strictly less than the kind of the datatype.
For instance, we may define a linear datatype containing unrestricted
parts.
On the contrary, it is forbidden to include affine elements in an unrestricted
datatype.
Here is the definition of a linear lists. The objects inside the list do not have to be linear.

@@

Ad-hoc polymorphism fits nicely in the framework of constrained
types and preserves all properties of our language such
as principal type inference. Its soundness is orthogonal to linear types
and has been explored in the literature~\citep{DBLP:journals/scp/Jones94}.

\subsection{Non-Lexical Lifetimes}

@@

Applied to the program above, only the first two lines would be annotated
to be ``in the region associated with @&x@'', but not the last line.
When typing the sequence, since the annotations are different, we will apply
the region rule to the right hand side.

>>>>

\subsection{Algebraic Datatypes}

Algebraic data types are a staple of functional programming and fit nicely
in our paradigm. Indeed, it is sufficient to ensure  that the kinds of
the constructor arguments are less than or equal to the kind of the datatype.
Hence, it is forbidden to include affine elements in an unrestricted
datatype, whereas the elements in a linear list may be linear or
unrestricted. 
Here is the definition of a datatype for linear lists.

@@

Ad-hoc polymorphism fits demonstrably in the \hmx framework of constrained
types and preserves all properties of our language such
as principal type inference. Its soundness is orthogonal to linear types
and has been explored in the literature~\citep{DBLP:conf/fpca/OderskyWW95}.

\subsection{Non-Lexical Regions}

@@

Applied to the program above, only the first two lines would be annotated
to be ``in the region associated with @&x@'', but not the last line.
Thanks to these annotations, when type checking the sequence we check
that the borrow does not escape the left-hand side (i.e., the second line).
